%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Georgia Institute of Technology} % Organization or Project
    {Atlanta, GA, USA} % Location
    {Spring 2022 - Spring 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Controlled-source electromagnetic (CSEM) and Magnetotellurics (MT) data collected by the NSF funded marine EM survey: \href{https://egl.eas.gatech.edu/projects/emage/}{\textit{ElectroMagnetic Alaskan GeoPRISMS Experiment}} (EMAGE)}
        \item {CSEM data processing and navigation.}
        \item {Inversion of the CSEM and MT data at the Alaska Subduction Zone jointly and individually.}
        \item {Comprehensive interpretation of inversion results from the Shumagin Gap and Semidi segments, Alaska-Aleutian subduction zone.}
        \item {Improve CSEM data processing and inversion visualizaiton.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Southern University of Science and Technology} % Organization or Project
    {Shenzhen, China} % Location
    {Aug. 2020 - June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Long-electrode electrical monitoring of shale gas fracturing and well casing integrity using surface electrical data and deep learning approaches. The work is a part of the National Natural Science Foundation of China funded research: \textit{High Resolution Imaging Monitoring of Shale Gas Fracturing Fluid using Long Electrode Electromagnetic Method}.}
        \item {Collaborated with the BGP company to develop a deep learning-based real-time hydraulic fracturing electrical monitoring system for the field experiment.}
        \item {Developed a GUI to customize the deep learning model architecture and parameters with a 3D visualization tool to visualize the results.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Visiting Undergraduate Student} % Job title
    {University of Naples Federico II} % Organization or Project
    {Napoli, Italy} % Location
    {Jan. 2018 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Study Abroad Scholarships}
        \item {Finished Bachelor thesis focusing on 2D site amplification effects modeling of the historical centre of Napoli under the supervision of Dr. Concettina Nunziata.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
