%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Field Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Near Trench Community Geodetic Experiment} % Organization or Project
    {Alaska-Aleutian Trench} % Location
    {June/July 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in 13-days seafloor geodetic instruments deployment at sea aboard the R/V Sikuliaq under \href{https://www.seafloorgeodesy.org/commexp}{\textit{Near-Trench Community Geodetic Experiment}.}}
        \item Deployed multiple GNSS-Acoustic benchmarks and transponders for measuring deformation and coupling along the Alaska-Aleutian megathrust. Two wavegliders were deployed for GNSS-A surveys and conductivity, temperature, and depth (CTD) data was collected for a sound speed profile.
        \item PIs on board: Andrew Newman, Georgia Institute of Technology and Dr. Spahr Webb, Lamont-Doherty Earth Observatory.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Kivu Project} % Organization or Project
    {Western Rwanda} % Location
    {May/June 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in 22-days land Magnetotellurics field work under an NSF funded collaborative research: \href{https://avnewman.github.io/KIVU/}{\textit{Constraining transient magma intrusion processes in the Nyiragongo-Kivu continental rift zone}.}}
        \item PIs: Dr. Andrew Newman and Dr. Samer Naif, Georgia Institute of Technology.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Seismology field work} % Organization or Project
    {Summerville, SC, USA} % Location
    {May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in 4-days nodal seismic deployment for understanding seismicity distribution within the South Eastern United States.}
        \item PI: Dr. Zhigang Peng, Georgia Institute of Technology.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Oceanographic field study} % Organization or Project
    {Savannah, GA, USA} % Location
    {May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in Ocean Science and Engineering (OSE) retreat and collaborative communication with the Skidaway Institute of Oceanography (SkIO), University of Georgia.}
        \item {One day on board the R/V Savannah to learn the basic practical knowledge of oceanography.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Seismology class field trip} % Organization or Project
    {Columbia, SC, USA} % Location
    {Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in 4-days nodal seismic deployment near the town of Elgin to study the tremors
        \item EAS 6314/4314 Seismology (Fall Semester 2022) given by Dr.Zhigang Peng, Georgia Institute of Technology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Marine electromagnetic survey HT-RESIST} % Organization or Project
    {Hikurangi Trench} % Location
    {Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in 2nd cruise of the \href{https://egl.eas.gatech.edu/projects/resist/}{\textit{Hikurangi Trench Regional Electromagnetic Survey to Image the Subduction Thrust} (HT-RESIST)} aboard R/V Roger Revelle.}
        \item {Ocean bottom electromagnetic stations recovery.}
        \item PIs: Dr. Samer Naif and Dr. Kerry Key, Columbia Univeristy Lamont-Doherty Earth Obs.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Long-electrode electrical monitoring of shale gas fracturing} % Organization or Project
    {Weiyuan, China} % Location
    {May/June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Software development and test for the long-electrode electrical monitoring method.}
        \item {Real-time hydraulic fracturing electrical monitoring data collection, collaborating with BGP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Long-electrode electrical method validation experiment} % Organization or Project
    {Huaibei, China} % Location
    {Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {3-days field work for collecting long-electrode electrical data with collaborators from China University of Mining and Technology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Job title
    {Field work} % Organization or Project
    {Eastern Tibetan Plateau, China} % Location
    {Spet. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participation in scouting part of the MT field work: India-Asia collision process through a study of Gongga Shan.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Graduate Student} % Job title
%     {Field work} % Organization or Project
%     {Huizhou, China} % Location
%     {Jan. 2020} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Participation in 6-days field work for land MT instrument comparison experiment.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {Undergraduate Student} % Job title
    {Field trip} % Organization or Project
    {Xinwen, China} % Location
    {June 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {12 days field trip for undergraduate course: Fundamentals of Geology.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
