%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

  \fontsize{11pt}{1.3em}\selectfont
  \begin{itemize}[leftmargin=2.5ex]
    \item {\textbf{Li, Y.}, S. Naif, D. Cordell, K. Key, R. L. Evans, S. Constable, D. J. Shillington, and A. Becel (2024). “Megathrust heterogeneity 
    revealed by Electromagnetic Data at the Aleutian-Alaska Subduction Zone”. The 26th EM Induction Workshop 2024, Beppu, Japan (Oral)}
    \item {\textbf{Li, Y.}, S. Naif, D. Cordell, K. Key, R. L. Evans, S. Constable, D. J. Shillington, and A. Becel (2023). “Electromagnetic Study
    of Fluid Distribution at the Aleutian-Alaska Subduction Zone”. AGU Annual Meeting 2023, San Francisco, CA (Oral)}
    \item {Naif, S., \textbf{Y. Li}, K. Key, R. Evans, S. Constable, and D. Cordell (2021). “Preliminary results from the Electromag-
    netic Alaskan GeoPRISMS Experiment (E-MAGE)”. AGU Fall Meeting 2021, New Orleans, LA (Poster)}
    \item {\textbf{Li, Y.} and D. Yang (2020), Monitoring the integrity of steel well casings using electrical data on the surface”. SEG 2020 Work-
    shop: 2nd SEG Borehole Geophysics Workshop, Virtual (Poster)}
    \item {\textbf{Li, Y.} and D. Yang (2020). “Imaging of steel casing’s conductivity using surface electrical data and a deep learning
    approach”. SEG International Exposition and 90th Annual Meeting, Virtual (Poster)}
    \item {\textbf{Li, Y.} and D. Yang (2019). “Fast electrical imaging of injected fluid in hydraulic fracturing using a practical inter-
    active parameter estimation method”. SEG International Exposition and 89th Annual Meeting, San Antonio, TX (Oral)}
  \end{itemize}

  % \nocite{*} % Include all entries from the BibTeX file in the bibliography
  % \printbibliography[heading=none, type=inproceedings] % Print the bibliography without a heading

%---------------------------------------------------------
\end{cvparagraph}
